### 2023-09-02 sections/2-methods.tex
misc changes

With these concepts defined, we can now pose the $k$- and $\rho$- nearest neighbors search problems.
Given a query $q$, along with a distance function $f$ defined on a dataset $\textbf{X}$, $k$-nearest neighbors search aims to find 
the set $S_q$ such that  $|S_q| = k$ and $\forall x \in \textbf{X} \setminus S_q$, $f(x, q) \leq \max\{f(y, q): y \in S_q \}$; that is,
for a given $k$, find the $k$ closest points to $q$ in $ \textbf{X}$.
We also have the $\rho$-nearest neighbors search problem, which aims to find the set $\{x \in \textbf{X}: f(q, x) \leq \rho \}$; that is, 
find all points in $\textbf{X}$ that are at most a distance $\rho$ from $q$.

We define \emph{singletons} as clusters which either contain a single point (i.e., have cardinality 1) or which contain 
many instances of the same point (i.e., have cardinality greater than 1 but contain only one unique point). Singletons clearly 
have zero radius, and so $\delta_{max}  = \delta = \delta_{min}$ for these clusters. Hence, we sometimes overload the above 
notation to refer to distance from a query to a point; in these cases, we also have that $\delta_{max} = \delta = \delta_{min}$.

@@

For a cluster $C$ with $|C|$ points, we begin by computing a 
random sample of $\sqrt{|C|}$ of its points, and computing pairwise distances 
between all points in the sample. Based on those pairwise distances, we compute the \emph{geometric median} of this sample; 
that is, the point which minimizes the sum of distances to all other points in the sample. This geometric median 
is $C$'s \emph{center}. The \emph{radius} of $C$ is the maximum distance from any point in $C$ to its center.
The point $l$ which is responsible for that radius (i.e., the furthest point from the center) is designated the \emph{left pole}, and the point $r$ which is furthest
from $l$ is designated the \emph{right pole}. We then partition the cluster into a \emph{left child} and \emph{right child}, where the 
left child contains all points in the cluster which are closer to $l$ than to $r$, and the right child contains all 
points in the cluster which are closer to $r$ than to $l$. Without loss of generality, we assign to the left child 
those points which are equidistant from $l$ and $r$. Starting from a root-cluster containing the entire dataset, we 
repeat this procedure until each leaf contains only one datum or some other user-specified stopping criterion 
is met.

This process is described in Algorithm \ref{alg:partition}.

@@

In this case, Cluster Partition will select a maximally distant pair of points to use as poles, i.e., it will choose one of the $d$ axes along
which to split the cluster into two children. 
After one application of Algorithm \ref{alg:partition}, the maximum pairwise distance along that axis will be
bounded above by $R$. 
The next recursive Cluster Partition will select another of the $d$ axes. 
Thus, after at most $d$ applications of Algorithm \ref{alg:partition}, the
maximum pairwise distance along each axis will be bounded above by $R$. 
The overall (i.e., not restricted to one axis) maximum pairwise distance 
will be bounded above by $R\sqrt{2}$ by, for example, two instances that lie at the extrema of different axes.

@@

We begin by randomly partitioning the dataset into $s$ shards, where $s$ is determined based 
on some naive auto-tuning. On the first shard, we perform 
$k$-nearest neighbors search using one of the four algorithms described in Section~\ref{subsec:methods:knn-search}.
The result of this search will give us the $k$ closest neighbors to the query \emph{in the first shard}. We then take the furthest of 
those $k$ neighbors and use its distance from the query as the radius for use with $\rho$-nearest neighbors search (see Section~\ref{subsec:methods:rnn-search}) 
on each remaining shard. We then take the union of the results of these $\rho$-nearest neighbors searches, along with the $k$ neighbors
from the first shard, and then linear search over those points to find the actual $k$ nearest neighbors.

Note that the size of the shards is not necessarily consistent; it is often optimal to have the first shard be smaller than the others,
since the first shard is the only one for which we perform $k$-nearest neighbors search. However, making this first shard too small
introduces the risk of significantly overestimating the radius, resulting in much slower $\rho$-nearest neighbors search on the subsequent shards.
Finding the precise optimal ratio between the size of the first shard and the size of the remaining shards, as well 
as computing the expected level of error between the distance from the $k$-th closest neighbor in the first shard and the 
actual $k$-th closest neighbor, are topics for future work.

@@

We conduct $\rho$-nearest neighbors search as described in \cite{ishaq2019clustered}, but 
with the following improvement: when a cluster overlaps with the query ball, instead of  
always proceeding with both of its children, we proceed only with those children which 
also overlap with the query ball. This improvement is demonstrated in Algorithm \ref{alg:rnn}.

@@

Let $H$ be the set of nearest neighbors found thus far.
Search starts with a radius $m$ equal to the radius of the root cluster divided by
the cardinality of the dataset. We perform $\rho$-NN search with radius $m$. 
If no points are within a distance $m$ of the query, we increase the radius by a factor of arg
2 and perform $\rho$-NN search again, repeating until at least one point is found, i.e., 
until $|H| > 0$.

Once $|H| > 0$, we continue to perform $\rho$-NN search, but instead of 
increasing the radius by a factor of 2 on each iteration, we increase it by a factor determined 
by the local fractal dimension in the region of the dataset around the query ball. 
In particular, 
we increase the radius by a factor of 
\begin{equation} \argmin \left(2, \left({\frac{k}{|H|}}\right)^{\frac{1}{\mu}}\right) \label{2} \end{equation}
where $\mu$ is the harmonic mean of the local fractal dimensions (abbreviated lfd in algorithm below) of 
each cluster which contains one of the nearest neighbors found thus far. We use the harmonic mean to 
ensure that $\mu$ is not dominated by outlier clusters with very high fractal dimension. 
Intuitively, the factor by which we increase the radius should be \emph{inversely} related to the number of points found so far. 
Additionally, when the local fractal dimension at the radius scale from the previous iteration is low, this suggests that the data 
are relatively concentrated in that region; in other words, a small increase in the radius would likely encounter unoccupied space around the manifold, so a larger radius increase is needed. Thus, in this case, the factor of radius increase should be \emph{directly} related to the 
local fractal dimension. Once $|H| >= k$, we return the $k$ closest points.

\begin{algorithm} % enter the algorithm environment
    \caption{Repeated$\rho$-NN(\emph{root, query, k})} % give the algorithm a caption
    \label{alg:knn-by-rnn} % and a label for \ref{} commands later in the document
    \begin{algorithmic} % enter the algorithmic environment
        \STATE $H \Leftarrow$ $\emptyset$
        \STATE $m \Leftarrow$ $\frac{root.radius}{|root|}$
        \WHILE {$|H| = 0$}
            \STATE $H.push(\rho$-NN$(root, query, m)$)
            \STATE $m \Leftarrow 2m$
        \ENDWHILE
        \WHILE {$|H| < k$}
            \STATE $Q \Leftarrow \{ C: \exists p \in H \land p \in C \}$
            \STATE $\mu \Leftarrow |Q| \sum_{C \in Q} \frac{1}{C.lfd} $
            \STATE $m \Leftarrow \argmin \left(2, \left({\frac{k}{|H|}}\right)^{\frac{1}{\mu}}\right)$
            \STATE $H.push(\rho$-NN$(root, query, m)$)
        \ENDWHILE
        \STATE $H.sort()$
        \STATE Return $H[0], H[1], \cdots H[k-1]$
    \end{algorithmic}
    \end{algorithm}

@@

Our complexity bounds for $k$-NN by Repeated $\rho$-NN rely on the assumption that the query point is sampled from the same distribution
(i.e. arises from the same generating phenomenon) as the rest of the data. From this assumption, we can infer that the local fractal dimension
at the query point is not significantly different from the mean local fractal dimension of clusters nearby the query.

@@

In ~\cite{ishaq2019clustered}, we claimed that the complexity of coarse search for $\rho$-NN is $\mathcal{O}(\log{2}$\mathcal{N}_{\hat{r_c}}(D)$)$, 
where $m$\mathcal{N}_{\hat{r_c}}(D)$$ is the metric entropy of the dataset $D$. 
To adjust this bound for $k$-NN by Repeated $\rho$-NN, we must estimate the number of iterations 
of $\rho$-NN needed to find at least $k$ neighbors.

Based on the assumption that the local fractal dimension at the query point is not significantly different than that of 
nearby clusters, the factor from Equation \ref{2} suggests that in the expected case, we need only two iterations of 
$\rho$-NN to find $k$ neighbors: one iteration to find at least one neighbor, and the one more to find enough remaining neighbors.
Since this is a constant factor, it does not affect the asymptotic complexity of coarse search, and thus we have that 
the complexity of coarse search for $k$-NN by Repeated $\rho$-NN is $\mathcal{O}(\log_2{m})$.

@@

~\cite{yu2015entropy} showed that $|F| \leq \gamma |B(q, r')|\left(\frac{r'+ 2r_c}{r'}\right)^d$, where $\gamma$ is a constant. 
By definition of 
$r'$, we have that $|B(q, r')| = k$. Thus, we have that $|F| \leq \gamma k\left(\frac{r'+ 2r_c}{r'}\right)^d$.

It remains to provide an estimate for $r'$. 
To do this, we once again rely on the assumption that the query is from the same distribution as the rest of the data, 
and thus the local fractal dimension at the query point is not significantly different than that of nearby clusters.

@@

By ~\ref{2}, we then have that \begin{equation} d_i = \frac{\log{}\frac{|C_i|}{k}}{\log{}\frac{r_i}{r'}}. \label{4} \end{equation}

@@

Putting our bounds for coarse and fine search together, we have that $k$-NN by Repeated $\rho$-NN has 
$\mathcal{O}\left(\log_2{\mathcal{N}_{\hat{r_c}}(D)} + k\left(\frac{r_i\left(\frac{k}{|C_i|}\right)^{\frac{1}{d_i}}+ 2r_c}{r_i\left(\frac{k}{|C_i|}\right)^{\frac{1}{d_i}}}\right)^d\right)$ 
time complexity, where $\mathcal{N}_{\hat{r_c}}(D) is the metric entropy of the dataset, $d$ is the dimensionality of the dataset, $r_i$ is the radius of some cluster $C_i$
near the query ball, $d_i$ is the local fractal dimension of $C_i$, $r_c$ is the radius of leaf clusters, and $k$ is the number of nearest neighbors.

\subsubsection{Sieve Search}
\label{subsubsec:methods:knn-search:sieve}
With Sieve Search, we begin by letting $Q$ be a list containing the root cluster. 
While $Q$ contains at least one cluster (i.e., $Q$ is not a list of only points), we repeat the process described in 
the following paragraphs.

@@

We then remove from $Q$ any element whose $\delta_{min}$ is greater than $\tau$. Then, for each element left 
in $Q$, if it is a leaf or contains $k$ or fewer points, we remove it and all of its points to $Q$. Finally, we
replace all remaining non-leaf clusters in $Q$ with their children.

@@

\subsubsection{Sieve Search with Separate Centers}
\label{subsubsec:methods:knn-search:sieve2}
Sieve Search with Separate Centers is the same as Sieve Search, but with the following modification: clusters 
in $Q$ are represented twice-- once as their center and once as the rest of their points. 
Because we have that for any cluster $C$, $C.\delta \leq C.\delta_{max}$, representing the cluster 
center separately from the rest of the points causes the threshold $\tau$ to decrease more quickly, 
thus allowing us to eliminate some clusters from $Q$ earlier in the process. More discussion about 
when this algorithm is preferable to Sieve Search is in Section 4: Results.

@@

With Greedy Sieve, we first let $Q$ be a min queue of clusters based on $\delta_{min}$. We initialize $Q$ with the root cluster.
Let $H$ be a fixed-size ($k$) max queue of points based on $\delta$. This queue starts empty.

While $H$ has fewer than $k$ clusters or $\delta$ of the top priority element in $H$ is greater 
than $\delta_{min}$ of the top priority element in $Q$, we do the following:
\begin{enumerate}
\item While the top priority element $q$ in $Q$ is not a leaf, pop $q$ from $Q$ and push its children.
\item For each point $p \in q$, push $p$ to $H$. 
\item Pop from $H$ until $H$ has $k$ points. 
\end{enumerate}
After this process, the points left in $H$ are the $k$ nearest neighbors of $q$.

This process is described in Algorithm \ref{alg:greedy_search}.

\begin{algorithm} 
\caption{GreedySearch(\emph{root, query, k})} 
\label{alg:greedy_search} 
\begin{algorithmic}
    \STATE $Q \Leftarrow$ priority queue
    \STATE $Q.push(root)$
    \STATE $H \Leftarrow$ priority queue
    \WHILE{$|H| < k \lor H.pop.\delta > Q.pop.\delta_{min}$}
        \WHILE{$\neg Q.pop.isLeaf$}
            \STATE $[l, r] \Leftarrow Q.pop().children$
            \STATE $Q.push([l, r])$
        \ENDWHILE
        \STATE $leaf \Leftarrow Q.pop()$
        \STATE $H.push(leaf)$
        \WHILE{$|H| > k$}
            \STATE $H.pop()$
        \ENDWHILE
    \ENDWHILE
    \STATE Return $H$
\end{algorithmic}
\end{algorithm}

@@

The complexity of Sieve Search is dominated by the complexity of our modified Quicksort Partition algorithm,
which, like the original Quicksort partition algorithm described in~\cite{10.1093/comjnl/5.1.10}, has $\mathcal{O}(n)$ complexity, 
where $n$ is the length of the input list. While the cardinality of clusters is greater than $k$, 2 is bounded 
above by 2, as $Q$ will contain at most two clusters (assuming the worst case, which is a balanced clustering). 
Once the cardinality of clusters in $Q$ is less than or equal to $k$, the cardinality of $Q$ is bounded above 
by $2k$, since, in the worst case, every cluster is a non-leaf and

>>>>

@@

For a cluster $C$ with $|C|$ points, we begin by computing a 
random sample of $\sqrt{|C|}$ of its points, and computing pairwise distances 
between all points in the sample. Based on those pairwise distances, we compute the \emph{geometric median} of this sample; 
that is, the point which minimizes the sum of distances to all other points in the sample. This geometric median 
is $C$'s \emph{center}. The \emph{radius} of $C$ is the maximum distance from any point in $C$ to its center.
The point $l$ which is responsible for that radius (i.e., the furthest point from the center) is designated the \emph{left pole}, and the point $r$ which is furthest
from $l$ is designated the \emph{right pole}. We then partition the cluster into a \emph{left child} and \emph{right child}, where the 
left child contains all points in the cluster which are closer to $l$ than to $r$, and the right child contains all 
points in the cluster which are closer to $r$ than to $l$. Without loss of generality, we assign to the left child 
those points which are equidistant from $l$ and $r$. Starting from a root-cluster containing the entire dataset, we 
repeat this procedure until each leaf contains only one datum or some other user-specified stopping criterion 
is met. This process is described in Algorithm \ref{alg:partition}.

@@

In this case, Cluster Partition will select a maximally distant pair of points to use as poles, i.e., it will choose one of the $d$ axes along
which to split the cluster into two children. 
After one application of Algorithm \ref{alg:partition}, the maximum pairwise distance along that axis will be
bounded above by $R$. 
The next recursive Cluster Partition will select another of the $d$ axes. 
Thus, after at most $d$ applications of Algorithm \ref{alg:partition}, the
maximum pairwise distance along each axis will be bounded above by $R$. 
The overall (i.e., not restricted to one axis) maximum pairwise distance 
will be bounded above by $R\sqrt{2}$ by, for example, two instances that lie at the extrema of different axes. 
See Figure 1 for a concrete example.

@@

We begin by randomly partitioning the dataset into $s$ shards, where $s$ is determined based 
on some naive auto-tuning. On the first shard, we perform 
$k$-nearest neighbors search using one of the four algorithms described in Section~\ref{subsec:methods:knn-search}.
The result of this search will give us the $k$ closest neighbors to the query \emph{in the first shard}. We take the furthest of 
those $k$ neighbors and use its distance from the query as the radius to be used with $\rho$-nearest neighbors search (see Section~\ref{subsec:methods:rnn-search}) 
on each remaining shard. We then take the union of the results of these $\rho$-nearest neighbors searches, along with the $k$ neighbors
from the first shard, and then linear search over those points to find the actual $k$ nearest neighbors.

Note that the size of the shards is not necessarily consistent; it is often optimal to have the first shard be smaller than the others,
since the first shard is the only one for which we perform $k$-nearest neighbors search. However, making this first shard too small
introduces the risk of significantly overestimating the radius (i.e., the distance to the $k$-th ), resulting in much slower $\rho$-nearest neighbors search on the subsequent shards.
Finding the precise optimal ratio between the size of the first shard and the size of the remaining shards, as well 
as computing the expected level of error between the distance from the $k$-th closest neighbor in the first shard and the 
actual $k$-th closest neighbor, are topics for future work.

\subsection{The Search Problem}
\label{subsec:methods:general-search}
Having explained the clustering process, we can now pose the $k$- and $\rho$- nearest neighbors search problems.
Given a query $q$, along with a distance function $f$ defined on a dataset $\textbf{X}$, $k$-nearest neighbors search aims to find 
the set $S_q$ such that  $|S_q| = k$ and $\forall x \in \textbf{X} \setminus S_q$, $f(x, q) \leq \max\{f(y, q): y \in S_q \}$; that is,
for a given $k$, find the $k$ closest points to $q$ in $ \textbf{X}$.
We also have the $\rho$-nearest neighbors search problem, which aims to find the set $\{x \in \textbf{X}: f(q, x) \leq \rho \}$; that is, 
find all points in $\textbf{X}$ that are at most a distance $\rho$ from $q$.

We define a \emph{singleton} as a cluster which either contains a single point (i.e., has cardinality 1) or which contains 
multiple instances of the same point (i.e., has cardinality greater than 1 but contains only one unique point). A singleton clearly 
has zero radius, and so $\delta_{max}  = \delta = \delta_{min}$ for these clusters. Hence, we sometimes overload the above 
notation to refer to distance from a query to a point; in these cases, we also have that $\delta_{max} = \delta = \delta_{min}$.

@@

We conduct $\rho$-nearest neighbors search as described in \cite{ishaq2019clustered}, but 
with the following improvement: when a cluster overlaps with the query ball, instead of  
always proceeding with both of its children, we proceed only with those children which 
also overlap with the query ball. This improvement is described in Algorithm \ref{alg:rnn}.

@@

Let $H$ be the set of nearest neighbors found thus far.
Search starts with a radius $m$ equal to the radius of the root cluster divided by
the cardinality of the dataset. We perform $\rho$-NN search with radius $m$. 
If no points are within a distance $m$ of the query, we increase the radius by a factor of
2 and perform $\rho$-NN search again, repeating until at least one point is found, i.e., 
until $|H| > 0$.

Once $|H| > 0$, we continue to perform $\rho$-NN search, but instead of 
increasing the radius by a factor of 2 on each iteration, we increase it by a factor determined 
by the local fractal dimension in the region of the dataset around the query ball. 
In particular, 
we increase the radius by a factor of 
\begin{equation} \min \left(2, \left({\frac{k}{|H|}}\right)^{\frac{1}{\mu}}\right) \label{2} \end{equation}
where $\mu$ is the harmonic mean of the local fractal dimensions (abbreviated lfd in algorithm below) of 
each cluster which contains one of the nearest neighbors found thus far. We use the harmonic mean to 
ensure that $\mu$ is not dominated by outlier clusters with very high fractal dimension. 
Intuitively, the factor by which we increase the radius should be \emph{inversely} related to the number of points found so far. 
Additionally, when the local fractal dimension at the radius scale from the previous iteration is low, this suggests that the data 
are relatively concentrated in that region; in other words, a small increase in the radius would likely encounter unoccupied space around the manifold, so a larger radial increase is needed. Thus, the factor of radius increase should be \emph{directly} related to the 
local fractal dimension. Once $|H| >= k$, we return the $k$ closest points.

\begin{algorithm} % enter the algorithm environment
    \caption{Repeated$\rho$-NN(\emph{root, query, k})} % give the algorithm a caption
    \label{alg:knn-by-rnn} % and a label for \ref{} commands later in the document
    \begin{algorithmic} % enter the algorithmic environment
        \STATE $H \Leftarrow$ $\emptyset$
        \STATE $m \Leftarrow$ $\frac{root.radius}{|root|}$
        \WHILE {$|H| = 0$}
            \STATE $H.push(\rho$-NN$(root, query, m)$)
            \STATE $m \Leftarrow 2m$
        \ENDWHILE
        \WHILE {$|H| < k$}
            \STATE $Q \Leftarrow \{ C: \exists p \in H \land p \in C \}$
            \STATE $\mu \Leftarrow |Q| \sum_{C \in Q} \frac{1}{C.lfd} $
            \STATE $m \Leftarrow \min \left(2, \left({\frac{k}{|H|}}\right)^{\frac{1}{\mu}}\right)$
            \STATE $H.push(\rho$-NN$(root, query, m)$)
        \ENDWHILE
        \STATE $H.sort()$
        \STATE Return $H[0], H[1], \cdots H[k-1]$
    \end{algorithmic}
    \end{algorithm}

@@

Our complexity bounds for $k$-NN by Repeated $\rho$-NN rely on the assumption that the query point is sampled from the same distribution
(i.e. arises from the same generating phenomenon) as the rest of the data. Given the uses of $k$-NN search in practice, 
this assumption is not unreasonable. From this assumption, we can infer that the local fractal dimension
at the query point does not differ significantly from the mean local fractal dimension of clusters nearby the query.

@@

In ~\cite{ishaq2019clustered}, we claimed that the complexity of coarse search for $\rho$-NN is $\mathcal{O}(\log_2\mathcal{N}_{\hat{r_c}}(D))$, 
where $\mathcal{N}_{\hat{r_c}}(D)$ is the metric entropy of the dataset $D$. 
To adjust this bound for $k$-NN by Repeated $\rho$-NN, we must estimate the number of iterations 
of $\rho$-NN needed to find at least $k$ neighbors.

Based on the assumption that the local fractal dimension at the query point is not significantly different than that of 
nearby clusters, the factor from Equation \ref{2} suggests that in the expected case, we need only two iterations of 
$\rho$-NN to find $k$ neighbors: one iteration to find at least one neighbor, and the one more to find enough remaining neighbors.
Since this is a constant factor, it does not affect the asymptotic complexity of coarse search, and thus we have that 
the complexity of coarse search for $k$-NN by Repeated $\rho$-NN is $\mathcal{O}(\log_2\mathcal{N}_{\hat{r_c}}(D))$.

@@

The work in~\cite{yu2015entropy} showed that \begin{equation} |F| \leq \gamma |B(q, r')|\left(\frac{r'+ 2r_c}{r'}\right)^d \label{3} \end{equation} where $\gamma$ is a constant. 
By definition of 
$r'$, we have that $|B(q, r')| = k$. Thus, we have that \begin{equation} |F| \leq \gamma k\left(\frac{r'+ 2r_c}{r'}\right)^d. \label{4} \end{equation} It remains to provide an estimate for $r'$. 
To do this, we once again rely on the assumption that the query is from the same distribution as the rest of the data, 
and thus the local fractal dimension at the query point is not significantly different than that of nearby clusters.

@@

By ~\ref{2}, we then have that \begin{equation} d_i = \frac{\log{}\frac{|C_i|}{k}}{\log{}\frac{r_i}{r'}}. \label{5} \end{equation}

@@

Putting our bounds for coarse and fine search together, we have that $k$-NN by Repeated $\rho$-NN has 
$\mathcal{O}\left(\log_2{\mathcal{N}_{\hat{r_c}}(D)} + k\left(\frac{r_i\left(\frac{k}{|C_i|}\right)^{\frac{1}{d_i}}+ 2r_c}{r_i\left(\frac{k}{|C_i|}\right)^{\frac{1}{d_i}}}\right)^d\right)$ 
time complexity, where $\mathcal{N}_{\hat{r_c}}(D)$ is the metric entropy of the dataset, $d$ is the dimensionality of the dataset, $r_i$ is the radius of some cluster $C_i$
near the query ball, $d_i$ is the local fractal dimension of $C_i$, $r_c$ is the radius of leaf clusters, and $k$ is the number of nearest neighbors.

\subsubsection{Sieve Search}
\label{subsubsec:methods:knn-search:sieve}
In this algorithm, we begin by letting $Q$ be a list containing only the root cluster. 
While $Q$ contains at least one cluster (i.e., $Q$ is not a list of only points), we repeat the process described in 
the following paragraphs.

@@

We then remove from $Q$ any element whose $\delta_{min}$ is greater than $\tau$. Then, for each element left 
in $Q$, if it is a leaf or contains $k$ or fewer points, we remove it and add all of its points to $Q$. Finally, we
replace all remaining non-leaf clusters in $Q$ with their children.

@@

\subsubsection{Sieve Search with Separate Centers}
\label{subsubsec:methods:knn-search:sieve2}
This algorithm is the same as Sieve Search, but with the following modification: clusters 
in $Q$ are represented twice-- once as their center and once as the rest of their points. 
Because we have that for any cluster $C$, $C.\delta \leq C.\delta_{max}$, representing the cluster 
center separately from the rest of the points causes the threshold $\tau$ to decrease more quickly, 
thus allowing us to eliminate some clusters from $Q$ earlier in the process. More discussion about 
when this algorithm is preferable to Sieve Search is in Section 4: Results.

@@

With Greedy Sieve, we first let $Q$ be a min queue of clusters prioritized by $\delta_{min}$. We initialize $Q$ with the root cluster.
Let $H$ be a fixed-size ($k$) max queue of points prioritized by $\delta$. This queue starts empty.

While $H$ has fewer than $k$ clusters or $\delta$ of the top priority element in $H$ is greater 
than $\delta_{min}$ of the top priority element in $Q$, we do the following:
\begin{enumerate}
\item While the top priority element $q$ in $Q$ is not a leaf, pop $q$ from $Q$ and push its children to $Q$.
\item For each point $p \in q$, push $p$ to $H$. 
\item Pop from $H$ until $H$ has $k$ points. 
\end{enumerate}
After this process, the points left in $H$ are the $k$ nearest neighbors of $q$. This algorithm is described in Algorithm \ref{alg:greedy_search}.

\begin{algorithm} 
\caption{GreedySieve(\emph{root, query, k})} 
\label{alg:greedy_search} 
\begin{algorithmic}
    \STATE $Q \Leftarrow$ priority queue
    \STATE $Q.push(root)$
    \STATE $H \Leftarrow$ priority queue
    \WHILE{$|H| < k \lor H.peek.\delta > Q.peek.\delta_{min}$}
        \WHILE{$\neg Q.peek.isLeaf$}
            \STATE $[l, r] \Leftarrow Q.pop().children$
            \STATE $Q.push([l, r])$
        \ENDWHILE
        \STATE $leaf \Leftarrow Q.pop()$
        \STATE $H.push(leaf)$
        \WHILE{$|H| > k$}
            \STATE $H.pop()$
        \ENDWHILE
    \ENDWHILE
    \STATE Return $H$
\end{algorithmic}
\end{algorithm}

@@
